---
title: "GSS challange More Data"
author: "Dorothy Decker!"
date: "7/3/2023"
output: html_document
---







```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
GSS <-read.dta(file="GSS2016.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,cappun)
mydata <- na.omit(mydata)
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

Is attitude toward capitol punishment (cappun) independent of race (race)?
If not, then whose view differs from whom??

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

#### Plot barplots tigerstats way

```{r}
barchartGC(~race + cappun,data=mydata)
barchartGC(~race + cappun,data=mydata, type="percent")

```

Looking at the tigerstats graphical data, we can observe that white people are more in favor of capital punishment in comparison to the other races being observed. While black people oppose capital punishment in comparison to the other races.

## Now with The Most data (fewer variables gives more data points)



### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

### Numerical Summaries  

```{r}
table1 <- xtabs(~race + cappun, data=mydata)
rowPerc(table1)
colPerc(table1)
```


The whites are in favor with 65.10% of capital punishment, while 34.90% of whites oppose. 57.37% of blacks oppose capital punishment, with only 42.63% in favor. In the other category, we can see 55.20% oppose, with 44.80% in favor. Among these numerical summaries, we can see that of all the races, the black category oppose capital punishment the most, and white category is in favor in comparison to the other races.


## Now with More data



## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->



```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

The P-value is 2.2e-16, this is very low, which can further conclude there is a statistical difference among the races. 

```{r}
fisherXY(mydata$race,mydata$cappun)
```

Yes, white differ from the other categories. We can see there is a statistical difference. Every race is different from every other race in this data set. The white race still holds the highest in favor of capital punishment. 



## More data version


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->



In conclusion, from doing both branches of data, we can see that with more data, we can find more differences between the data. In this set of data we were given 2867 data sets, and were able to find that there is a difference between each race. While in the second data set only two races are really different. This master branch has a more significant difference between the races, each one is different from eachother. 
